Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives

### 2015-01-28 paper/Diversity_MS.tex
Separate submission folder, table labelling in supplementary
Fixed referencing
Added M jobihley reference

\subsection{Data collection}
	One of us (SF) collected data from five museums: Natural History Museum, London (BMNH), Smithsonian Institute Natural History Museum, Washington D.C. (SI), American Museum of Natural History, New York (AMNH), Museum of Comparative Zoology, Cambridge M.A. (MCZ) and Field Museum of Natural History, Chicago (FMNH). We used the taxonomy in Wilson \& Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for the recently discovered tenrec species \textit{Microgale jobihely}. We photographed all of the tenrec and golden mole skulls available in the collections. This included 31 of the 34 species in the tenrec Family \citep{Olson2013} and 12 of the 21 species of golden moles \citep{Wilson2005}.

@@

	We used a combination of landmark and semilandmark analysis approaches to assess the shape variability in the skulls.  We used the TPS software suite \citep{Rohlf2013} to digitise landmarks and curves on the photos. We set the scale on each image individually to standardise for the different camera heights used when photographing the specimens. We created separate data files for each of the three morphometric analyses (dorsal, ventral and lateral views). One of us (SF) digitised landmarks and semilandmark points on every image individually. Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis. Our final data sets included photographs of 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).

@@

%********************************

%\bibliographystyle{systbio} 
%I made my own bst style file but it doesn't fix the formatting issues
	%I answered  yes for using an & instead of and in author lists and to have journal names in italics but it's not working
\bibliographystyle{refstyle2}

>>>>

\subsection{Data collection}
	One of us (SF) collected data from five museums: Natural History Museum, London (BMNH), Smithsonian Institute Natural History Museum, Washington D.C. (SI), American Museum of Natural History, New York (AMNH), Museum of Comparative Zoology, Cambridge M.A. (MCZ) and Field Museum of Natural History, Chicago (FMNH). We used the taxonomy in Wilson \& Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for the recently discovered tenrec species \textit{Microgale jobihely} \citep{Goodman2006}. We photographed all of the tenrec and golden mole skulls available in the collections. This included 31 of the 34 species in the tenrec Family \citep{Olson2013} and 12 of the 21 species of golden moles \citep{Wilson2005}.

@@

	We used a combination of landmark and semilandmark approaches to assess the shape variability in the skulls.  We used the TPS software suite \citep{Rohlf2013} to digitise landmarks and curves on the photos. We set the scale on each image individually to standardise for the different camera heights used when photographing the specimens. We created separate data files for each of the three morphometric analyses (dorsal, ventral and lateral views). One of us (SF) digitised landmarks and semilandmark points on every image individually. Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis. Our final data sets included photographs of 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).

@@

%********************************
%Custom bst file
\bibliographystyle{refstyle}
